Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-01 paper/paper.qmd
added reference to measurement

After gathering the responses, the data is subjected to thorough
cleaning and validation procedures to rectify inconsistencies and handle
any missing information. This step is crucial for ensuring that the
dataset accurately mirrors the electorate's sentiments. Each entry in
the finalized dataset reflects an individual's viewpoint at a given
moment, enabling a detailed analysis of the factors that shape public
opinion as the election nears. This structured methodology effectively
converts subjective opinions into measurable data, providing valuable
insights into voter behavior and preferences.

>>>>

After gathering the responses, the data is subjected to thorough
cleaning and validation procedures to rectify inconsistencies and handle
any missing information. This step is crucial for ensuring that the
dataset accurately mirrors the electorate's sentiments. Following data
cleaning, polling results are aggregated to smooth out individual poll
biases and mitigate random error. This aggregation process leverages
weighting based on poll quality, sample size, recency, and the historical
accuracy of each polling agency, as seen in FiveThirtyEight’s approach
(Silver, 2018; Jackman, 2005). By combining multiple polls, the aggregation
method produces a more reliable picture of public opinion trends over time.

Each entry in the finalized dataset reflects an individual's viewpoint
at a given moment, enabling a detailed analysis of the factors that
shape public opinion as the election nears. This structured methodology
effectively converts subjective opinions into measurable data, providing
valuable insights into voter behavior and preferences.
